---
title: "heatmap_AKT_ordered"
author: "Jacqui Perkinson"
date: "7/27/2019"
output: html_document
---

Load required packages

```{r}
library(dplyr)
library(gplots)
```

Source code for modified heatmap.2 function (called heatmap.mik)

```{r}
source('~/Desktop/Gastric_Cancer_Datasets/heatmap-mik.R')
```

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/expDat_clinDat_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/venn_AKT_genelists_output.Rdata")
```

Generate a random sample of 20 from the total number of rows in expDat

```{r}
set.seed(1111)
randSamp <- sample(1:nrow(gse62254_expDat), 20)
```

Extract genes using the random sample

```{r}
rand_geneList <- rownames(gse62254_expDat)[randSamp]
```

Print gene list

```{r}
rand_geneList
```

Extract expression data for the genes in the list

```{r}
rand_geneDat <- gse62254_expDat[match(rand_geneList, rownames(gse62254_expDat)),]
```

Standardise to mean 0, sd 1, and set observation above/below 3/-3 to 3 or -3

```{r}
rand_hm <- t(apply(rand_geneDat, 1, scale, scale=T))
rand_hm[rand_hm > 3] <- 3
rand_hm[rand_hm < -3] <- -3
```

Extract data for CDH1, AKT1, AKT3

```{r}
cdh1Dat <- gse62254_expDat["CDH1",]
akt1Dat <- gse62254_expDat["AKT1",]
akt3Dat <- gse62254_expDat["AKT3",]
akt2Dat <- gse62254_expDat["AKT2",]
```

Create colour matrix for teh above three genes

```{r}
columnColours <- rbind(bluered(ncol(gse62254_expDat))[rank(cdh1Dat)],
                       bluered(ncol(gse62254_expDat))[rank(akt1Dat)],
                       bluered(ncol(gse62254_expDat))[rank(akt3Dat)])
rownames(columnColours) <- c("CDH1", "AKT1", "AKT3")
```

Heatmap with column order from clustering

```{r}
heatmap.mik(rand_hm, trace='none', scale='none', col=bluered(50), ColSideColors = columnColours)
```

Heatmap with column order from CDH1

```{r}
cdh1_ord <- order(cdh1Dat)
heatmap.mik(rand_hm[,cdh1_ord], trace='none', scale='none', col=bluered(50), ColSideColors = columnColours[,cdh1_ord], Colv=FALSE)
```




```{r}
AKT_geneList <- c("AKT1", "AKT2", "AKT3")
```

Print gene list

```{r}
AKT_geneList
```

Extract expression data for the genes in the list

```{r}
AKT_geneDat <- gse62254_expDat[match(AKT_geneList, rownames(gse62254_expDat)),]
```

Standardise to mean 0, sd 1, and set observation above/below 3/-3 to 3 or -3

```{r}
AKT_hm <- t(apply(AKT_geneDat, 1, scale, scale=T))
AKT_hm[AKT_hm > 3] <- 3
AKT_hm[AKT_hm < -3] <- -3
```

Create colour matrix for the above three genes

```{r}
cdh_columnColours <- rbind(bluered(ncol(gse62254_expDat))[rank(cdh1Dat)])
rownames(cdh_columnColours) <- "CDH1"
```

Heatmap with column order from clustering

```{r}
heatmap.mik(AKT_hm, trace='none', scale='none', col=bluered(50), ColSideColors = cdh_columnColours,
            keysize=0.5, cexRow=0.5)
```

Heatmap with column order from CDH1

```{r}
#pdf("51hm_ordered_cdh.pdf", height=4)
heatmap.mik(AKT_hm[,cdh1_ord], trace='none', scale='none', col=bluered(50), ColSideColors = cdh_columnColours[,cdh1_ord], Colv=FALSE)
#dev.off()
```










Print gene list

```{r}
AKT3_geneList <- AKT3_final
```

Extract expression data for the genes in the list

```{r}
AKT3_geneDat <- gse62254_expDat[match(AKT3_geneList, rownames(gse62254_expDat)),]
```

Standardise to mean 0, sd 1, and set observation above/below 3/-3 to 3 or -3

```{r}
AKT3_hm <- t(apply(AKT3_geneDat, 1, scale, scale=T))
AKT3_hm[AKT3_hm > 3] <- 3
AKT3_hm[AKT3_hm < -3] <- -3
```

Create colour matrix for the above three genes

```{r}
akt_columnColours <- rbind(bluered(ncol(gse62254_expDat))[rank(cdh1Dat)],
                       bluered(ncol(gse62254_expDat))[rank(akt1Dat)],
                       bluered(ncol(gse62254_expDat))[rank(akt3Dat)])
rownames(akt_columnColours) <- c("CDH1", "AKT1", "AKT3")
```

Heatmap with column order from clustering

```{r}
heatmap.mik(AKT3_hm, trace='none', scale='none', col=bluered(50), ColSideColors = akt_columnColours)
```

Heatmap with column order from CDH1 and AKT3

```{r}
heatmap.mik(AKT3_hm[,cdh1_ord], trace='none', scale='none', col=bluered(50), ColSideColors = akt_columnColours[,cdh1_ord], Colv=FALSE)
```

```{r}
#pdf("51hm_ordered_cdhwithakt3.pdf", height=4)
akt3_ord <- order(akt3Dat)
heatmap.mik(AKT3_hm[,akt3_ord], trace='none', scale='none', col=bluered(50), ColSideColors = akt_columnColours[,akt3_ord], Colv=FALSE)
#dev.off()
```

```{r}
a <- c("AKT1", "AKT2", "AKT3", "EGFR", "EGFR", "EGFR", "EGFR")
b <- gse62254_expDat[match(a, rownames(gse62254_expDat)),]
c <- t(apply(b, 1, scale, scale=T))
c[c > 3] <- 3
c[c < -3] <- -3

columnColours_cdh <- rbind(bluered(ncol(gse62254_expDat))[rank(cdh1Dat)])
rownames(columnColours_cdh) <- "CDH1"

#pdf("3hm.pdf", height=4)
heatmap.mik(c[,cdh1_ord], trace='none', scale='none', col=bluered(50), ColSideColors = columnColours_cdh[,cdh1_ord], Colv=FALSE)
#dev.off()
```





