---
title: "heatmap_AKT"
author: "Jacqui Perkinson"
date: "7/27/2019"
output: html_document
---

Load required packages.

```{r message=FALSE}
library(dplyr)
library(gplots)
```

Load required objects.

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/venn_AKT_genelists_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/expDat_clinDat_output.Rdata")
```

Objects for heatmaps.

```{r}
genes51 <- AKT3_final
genes3498 <- AKT3_allsig
genes190 <- AKT1_final
g_expdat <- gse62254_expDat
t_expdat <- tcga_expDat
```

# Heatmap of 51 genes (associated with AKT3, filtered on fold change).

Heatmap of genes in GSE datset.

```{r}
#pdf("51hm_GEO.pdf", height=4)
g_htmap <- g_expdat[match(genes51, rownames(g_expdat)),]
dim(g_htmap)
g_htmap <- t(apply(g_htmap, 1, scale, scale = T))
g_htmap[g_htmap < -3] <- -3
g_htmap[g_htmap > 3] = 3
heatmap.2(g_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```

Heatmap of genes in TCGA datset.

```{r}
#pdf("51hm_TCGA.pdf", height=4)
t_htmap <- t_expdat[match(genes51, rownames(t_expdat)),]
dim(t_htmap)
t_htmap <- t(apply(t_htmap, 1, scale, scale = T))
t_htmap[t_htmap < -3] <- -3
t_htmap[t_htmap > 3] = 3
heatmap.2(t_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```

# Heatmap of 3498 genes (associated with AKT3, filtered on fold change).

Heatmap of genes in GSE datset.

```{r}
#pdf("3498hm_GEO.pdf", height=4)
g_htmap <- g_expdat[match(genes3498, rownames(g_expdat)),]
dim(g_htmap)
g_htmap <- t(apply(g_htmap, 1, scale, scale = T))
g_htmap[g_htmap < -3] <- -3
g_htmap[g_htmap > 3] = 3
heatmap.2(g_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```

Heatmap of genes in TCGA datset.

```{r}
#pdf("3498hm_TCGA.pdf", height=4)
t_htmap <- t_expdat[match(genes3498, rownames(t_expdat)),]
dim(t_htmap)
t_htmap <- t(apply(t_htmap, 1, scale, scale = T))
t_htmap[t_htmap < -3] <- -3
t_htmap[t_htmap > 3] = 3
heatmap.2(t_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```

# Heatmap of 190 genes (associated with AKT1, filtered on fold change).

Heatmap of genes in GSE datset.

```{r}
#pdf("190hm_GEO.pdf", height=4)
g_htmap <- g_expdat[match(genes190, rownames(g_expdat)),]
dim(g_htmap)
g_htmap <- t(apply(g_htmap, 1, scale, scale = T))
g_htmap[g_htmap < -3] <- -3
g_htmap[g_htmap > 3] = 3
heatmap.2(g_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```

Heatmap of genes in TCGA datset.

```{r}
#pdf("190hm_TCGA.pdf", height=4)
t_htmap <- t_expdat[match(genes190, rownames(t_expdat)),]
dim(t_htmap)
t_htmap <- t(apply(t_htmap, 1, scale, scale = T))
t_htmap[t_htmap < -3] <- -3
t_htmap[t_htmap > 3] = 3
heatmap.2(t_htmap, trace = 'none', scale ='none', col = bluered(50))
#dev.off()
```






