---
title: "metagene_AKT3_3498genes"
author: "Jacqui Perkinson"
date: "7/27/2019"
output: html_document
---

Load required packages.

```{r message=FALSE}
library(dplyr)
library(gplots)
```

Load required objects.

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/venn_AKT_genelists_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/expDat_clinDat_output.Rdata")
```

Objects for heatmaps.

```{r}
genes3498 <- AKT3_allsig
g_expdat <- gse62254_expDat
t_expdat <- tcga_expDat
```

# Metagene of 3498 genes (associated with AKT3, filtered on fold change).

### GSE expression data.

Expression data for 3498 genes.

```{r}
gse_keep_genes3498 <- which(rownames(g_expdat) %in% genes3498)
gse_expData_genes3498 <- g_expdat[gse_keep_genes3498,]
```

Scale the expression data.

```{r}
gse_gn3498_scaled <- t(apply(gse_expData_genes3498,1,function (x) (x-mean(x))/sd(x)))
gse_gn3498_scaled[gse_gn3498_scaled< -3] <- -3; gse_gn3498_scaled[gse_gn3498_scaled> 3] <- 3
```

Create a heatmap.

```{r}
#pdf("3498hm_GEO_premetagene.pdf", height=4)
heatmap.2(gse_gn3498_scaled, trace = "none", scale = "none", col = bluered(50), labRow = "", labCol = "", distfun = function(x) as.dist(1-cor(t(x))) )
#dev.off()
```

Create a metagene.

```{r}
gse_gn3498_metagene <- svd(gse_gn3498_scaled)$v[,1]
```

Rescale to 0,1 range.

```{r}
gse_gn3498_metagene_rank <- rank(gse_gn3498_metagene)/length(gse_gn3498_metagene)
```

Assign a colour scale (for the heatmap).

```{r}
gse_gn3498_metagene_col <- bluered(length(gse_gn3498_metagene))[rank(gse_gn3498_metagene)]
```

Order the columns based on metagene value - shows a gradient of expression summarised with each gene.

```{r}
#pdf("3498metagene_GEO.pdf", height=4)
gse_gn3498_metagene_ord <- order(gse_gn3498_metagene_rank)
heatmap.2(gse_gn3498_scaled[,gse_gn3498_metagene_ord], trace='none', scale='none', Colv=F,
          ColSideColors=gse_gn3498_metagene_col[gse_gn3498_metagene_ord], key=F, col=bluered(50),
          labCol= "", labRow= "")
#dev.off()
```

### TCGA expression data.

Expression data for 3498 genes.

```{r}
tcga_keep_genes3498 <- which(rownames(t_expdat) %in% genes3498)
tcga_expData_genes3498 <- t_expdat[tcga_keep_genes3498,]
```

Scale the expression data.

```{r}
tcga_gn3498_scaled <- t(apply(tcga_expData_genes3498,1,function (x) (x-mean(x))/sd(x)))
tcga_gn3498_scaled[tcga_gn3498_scaled< -3] <- -3; tcga_gn3498_scaled[tcga_gn3498_scaled> 3] <- 3
```

Create a heatmap.

```{r}
#pdf("3498hm_TCGA_premetagene.pdf", height=4)
heatmap.2(tcga_gn3498_scaled, trace = "none", scale = "none", col = bluered(50), labRow = "", labCol = "", distfun = function(x) as.dist(1-cor(t(x))) )
#dev.off()
```

Create a metagene.

```{r}
tcga_gn3498_metagene <- svd(tcga_gn3498_scaled)$v[,1]
```

Rescale to 0,1 range.

```{r}
tcga_gn3498_metagene_rank <- rank(tcga_gn3498_metagene)/length(tcga_gn3498_metagene)
```

Assign a colour scale (for the heatmap).

```{r}
tcga_gn3498_metagene_col <- bluered(length(tcga_gn3498_metagene))[rank(tcga_gn3498_metagene)]
```

Order the columns based on metagene value - shows a gradient of expression summarised with each gene.

```{r}
#pdf("3498metagene_TCGA.pdf", height=4)
tcga_gn3498_metagene_ord <- order(tcga_gn3498_metagene_rank)
heatmap.2(tcga_gn3498_scaled[,tcga_gn3498_metagene_ord], trace='none', scale='none', Colv=F,
          ColSideColors=tcga_gn3498_metagene_col[tcga_gn3498_metagene_ord], key=F, col=bluered(50),
          labCol= "", labRow= "")
#dev.off()
```

