---
title: "reactome_AKT"
author: "Jacqui Perkinson"
date: "7/26/2019"
output: html_document
---

Load required packages.

```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(reactome.db)
library(ReactomePA)
library(org.Hs.eg.db)
```

Load required objects.

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/venn_AKT_genelists_output.Rdata")
```

# Gene ontology using reactome.

### 51 gene list (AKT3 associated, filtered on fold change).

AKT3_final - convert to Entrez gene IDs

```{r}
AKT3_Entrez <- select(org.Hs.eg.db, keys = AKT3_final, columns = c("ENTREZID", "SYMBOL"), keytype = "SYMBOL")
AKT3_Entrez <- as.vector(AKT3_Entrez[,2])
```

Perform pathway analysis via reactomePA

```{r}
AKT3_rPAoverrep <- enrichPathway(gene = AKT3_Entrez, organism = "human", pvalueCutoff = 0.05, readable = T)
AKT3_rPAoverrep %>% as.data.frame() %>% View
#write.csv(AKT3_rPAoverrep, file = "51reactome.csv")
```

Plots

```{r}
pdf("reactome51.pdf")
#barplot(AKT3_rPAoverrep, showCategory = 10, font.size = 8)
dotplot(AKT3_rPAoverrep, showCategory = 10, font.size = 1)
dev.off()
```

### 3498 gene list (AKT3 associated, not filtered by fold change).

AKT3_allsig - convert to Entrez gene IDs

```{r}
allAKT3_Entrez <- select(org.Hs.eg.db, keys = AKT3_allsig, columns = c("ENTREZID", "SYMBOL"), keytype = "SYMBOL")
allAKT3_Entrez <- as.vector(allAKT3_Entrez[,2])
```

Perform pathway analysis via reactomePA

```{r}
allAKT3_rPAoverrep <- enrichPathway(gene = allAKT3_Entrez, organism = "human", pvalueCutoff = 0.05, readable = T)
allAKT3_rPAoverrep %>% as.data.frame() %>% head
#write.csv(allAKT3_rPAoverrep, file = "3498reactome.csv")
```

Plots

```{r}
pdf("reactome3498.pdf")
#barplot(allAKT3_rPAoverrep, showCategory = 11, font.size = 6)
dotplot(allAKT3_rPAoverrep, showCategory = 10, font.size = 2)
dev.off()
```

### 190 gene list (AKT1 associated, not filtered by fold change).

AKT1_final - convert to Entrez gene IDs

```{r}
AKT1_Entrez <- select(org.Hs.eg.db, keys = AKT1_final, columns = c("ENTREZID", "SYMBOL"), keytype = "SYMBOL")
AKT1_Entrez <- as.vector(AKT1_Entrez[,2])
```

Perform pathway analysis via reactomePA - not significant.

```{r}
AKT1_rPAoverrep <- enrichPathway(gene = AKT1_Entrez, organism = "human", pvalueCutoff = 0.05, readable = T, qvalueCutoff = 0.5)
AKT1_rPAoverrep %>% head
#write.csv(AKT1_rPAoverrep, file = "190reactome.csv")
```

Plots

```{r}
#pdf("reactome190.pdf")
#barplot(AKT1_rPAoverrep, showCategory = 11, font.size = 8)
#dotplot(AKT1_rPAoverrep, showCategory = 11, font.size = 4)
#dev.off()
```













