---
title: "siRNA_AKT_pathways"
author: "Jacqui Perkinson"
date: "7/27/2019"
output: html_document
---

Load required packages.

```{r message=FALSE}
library(dplyr)
```

Load all siRNA genes.

```{r}
allGenes <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/all_genes_tyler.csv")
```

# CD28_dependent_PI3K_Akt_signaling

```{r}
pdf("CD28_dependent_PI3K_Akt_signaling.pdf", height=4, width = 8)
a <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/CD28_dependent_PI3K_Akt_signaling.csv")

reactome <- a

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,max(c(d1,d2))), xlab="", ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:22,4])
d2max$x[which.max(d2max$y)]

alist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# Constitutive_signalling_by_aberrant_PI3K_in_cancer

```{r}
pdf("constitutive_signalling_by_aberrant_PI3K_in_cancer.pdf", height=4, width = 8)
b <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/constitutive_signalling_by_aberrant_PI3K_in_cancer.csv")

reactome <- b

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,max(c(d1,d2))),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:86,4])
d2max$x[which.max(d2max$y)]

blist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# G_beta_gamma_signalling_through_PI3Kgamma

```{r}
pdf("G_beta_gamma_signalling_through_PI3Kgamma.pdf", height=4, width = 8)
c <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/G_beta_gamma_signalling_through_PI3Kgamma.csv")

reactome <- c

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,max(c(d1,d2))),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,3,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:25,4])
d2max$x[which.max(d2max$y)]

clist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# Negative_regulation_of_the_PI3K_AKT_network

```{r}
pdf("negative_regulation_of_the_PI3K_AKT_network.pdf", height=4, width = 8)
d <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/negative_regulation_of_the_PI3K_AKT_network.csv")

reactome <- d

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,3),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:122,4])
d2max$x[which.max(d2max$y)]

dlist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# PI3K_AKT_activation

```{r}
pdf("PI3K_AKT_activation.pdf", height=4, width = 8)
e <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/PI3K_AKT_activation.csv")

reactome <- e

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,max(c(d1,d2))),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:9,4])
d2max$x[which.max(d2max$y)]

elist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off
```

# PI3K_AKT_signalling_in_cancer

```{r}
pdf("PI3K_AKT_signalling_in_cancer.pdf", height=4, width = 8)
f <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/PI3K_AKT_signalling_in_cancer.csv")

reactome <- f

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,max(c(d1,d2))),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:112,4])
d2max$x[which.max(d2max$y)]

flist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# PI3K_cascade

```{r}
pdf("PI3K_cascade.pdf", height=4, width = 8)
g <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/PI3K_cascade.csv")

reactome <- g

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,2.5),
  xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:50,4])
d2max$x[which.max(d2max$y)]

glist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# PI3K_events_in_ERBB3_signalling

```{r}
pdf("PI3K_events_in_ERBB3_signalling.pdf", height=4, width = 8)
h <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/PI3K_events_in_ERBB3_signalling.csv")

reactome <- h

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,2.5),
   xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:18,4])
d2max$x[which.max(d2max$y)]

hlist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# PI3K_events_in_ERBB4_signalling

```{r}
pdf("PI3K_events_in_ERBB4_signalling.pdf", height=4, width = 8)
i <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/PI3K_events_in_ERBB4_signalling.csv")

reactome <- i

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,2.5),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:11,4])
d2max$x[which.max(d2max$y)]

ilist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```

# PI5P_PP2A_and_IER3_regulate_PI3K_AKT_signalling

```{r}
pdf("Pi5P_PP2A_and_IER3_regulate_PI3K_AKT_signalling.pdf", height=4, width = 8)
j <- read.csv("~/Desktop/Gastric_Cancer_Datasets/Data/SL_tests/Pi5P_PP2A_and_IER3_regulate_PI3K_AKT_signalling.csv")

reactome <- j

MolNam <- as.character(reactome$MoleculeName)
react <- reactome[,-3]
MolNamSplit <- t(strsplit(MolNam, split = " ", fixed = TRUE) %>% as.data.frame())
react$Name <- MolNamSplit[,2]
geneCoordinates<-match(as.vector(react[,3]),as.vector(allGenes[,1]))
react_data<-allGenes[geneCoordinates,]
react_noNA<-na.omit(react_data)
react_noNA %>% dim

x<-allGenes
y<-react_noNA
mx<-quantile(x[,4],0.999)
mn<-quantile(x[,4],0.001)
ksp<-ks.test(x[,4], y[,4])$p.value
kst<-paste("KS p-value= ",round(ksp,4),sep='')
d1<-density(x[,4])$y
d2<-density(y[,4])$y
plot(density(x[,4]),col='blue',xlim=c(mn,mx), ylim=c(0,2.5),
    xlab="",ylab="Density", main = "", cex.lab=1.5, cex.axis=1.5)
legend(1.5,1.8,c("All","Reactome list"),fill=c(4,2), title=kst,cex=1.2)
lines(density(y[,4],na.rm=T),type='l',col='red')

d1max<-density(x[,4])
d1max$x[which.max(d1max$y)]
d2max<-density(y[1:115,4])
d2max$x[which.max(d2max$y)]

jlist <- react_data %>% filter(., fold.change.ratio.normalised.to.average.mock.across.plates < 0.85) %>% dplyr::select(., entrez.gene.name) %>% unlist() %>% as.vector() %>% unique()
dev.off()
```




# Pull genes from all pathways with a fold change ratio < 0.85 and combine into one vector. Ordered inhibitors for genes from this list.

```{r}
pathwaygenes <- c(alist, blist, clist, dlist, elist, flist, glist, hlist, ilist, jlist) %>% unique  
pathwaygenes
```

p-values <0.05

```{r}
pathwaygenes_p <- c(clist, flist, glist) %>% unique  
pathwaygenes_p %>% sort
```

FC ------------------------ 

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/GSE_AKT3_3rds_limma_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/TCGA_AKT3_3rds_limma_output.Rdata")
```

```{r}
tcga_rec_keep <- which(rownames(tcga_AKT3_tt_extr) %in% pathwaygenes)
tcga_rec_keep %>% length()

tcga_tt_rec_keygenes <- tcga_AKT3_tt_extr[tcga_rec_keep,]
tcga_tt_rec_keygenes %>% dim()
tcga_tt_rec_keygenes %>% head()

#write.csv(tcga_tt_rec_keygenes, file = "recTCGA.csv")
```

```{r}
gse_rec_keep <- which(rownames(gse_AKT3_tt_extr) %in% pathwaygenes)
gse_rec_keep %>% length()

gse_tt_rec_keygenes <- gse_AKT3_tt_extr[gse_rec_keep,]
gse_tt_rec_keygenes %>% dim()
gse_tt_rec_keygenes %>% head

#write.csv(gse_tt_rec_keygenes, file = "recGEO.csv")
```


