---
title: "TCGA_limma_AKT1_3rds"
author: "Jacqui Perkinson"
date: "7/19/2019"
output: html_document
---

Load required packages.

```{r}
library(here)
library(dplyr)
library(ggplot2)
library(limma)
library(org.Hs.eg.db)

options(width=80)
```

# Load TCGA setup objects

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/TCGA_setup.Rdata")
```

# Limma Analysis.

### Set up the high AKT1 and low AKT1 expression groups (low = 1/3 and high = 2/3) for limma analysis.

```{r}
AKT1_data_sorted <- sort(tcga_AKT1_data)
threshold_1 <- AKT1_data_sorted[138] # 7.207709
```

Split AKT1 expression data by 3rds, assign the groups "high = 1" or "low = 0".

```{r}
tcga_AKT1_data_extr <- ifelse(tcga_AKT1_data <= threshold_1, "0", "1")
tcga_AKT1_data_extr %>% table
tcga_AKT1_data_extr %>% head
```

### Find the differentially expressed genes between the AKT1 high and AKT1 low groups.

Create the design matrix and rename columns.

```{r}
tcga_AKT1_design_extr <- model.matrix(~ifelse(tcga_AKT1_data <= threshold_1, 0, 1))
colnames(tcga_AKT1_design_extr) <- c("low", "highVSlow")
tcga_AKT1_design_extr %>% head
```

Fit a linear model.

```{r}
tcga_AKT1_fit_extr <- lmFit(tcga_expDat, tcga_AKT1_design_extr)
tcga_AKT1_fit_extr <- eBayes(tcga_AKT1_fit_extr)
tcga_AKT1_tt_extr <- topTable(tcga_AKT1_fit_extr, coef = "highVSlow", adjust = "BH", n = nrow(tcga_expDat))
```

Preview topTable output.

```{r}
tcga_AKT1_tt_extr %>% dim
tcga_AKT1_tt_extr %>% head
```

Pull the significant differentially expressed genes between high AKT1 and low AKT1 expression groups.

```{r}
sum(tcga_AKT1_tt_extr$adj.P.Val<0.05)
```

Pull a list of the genes with an adjusted P value < 0.05.

```{r}
tcga_AKT1_sigGen_extr <- tcga_AKT1_tt_extr %>%  
  mutate(., Gene=rownames(tcga_AKT1_tt_extr)) %>% 
  filter(., adj.P.Val < 0.05) %>% 
  dplyr::select(., Gene)

tcga_AKT1_sigGen_extr %>% dim
tcga_AKT1_sigGen_extr %>% head
```

Significant genes with a FC above 2 (negative or positive).

```{r}
tcga_AKT1_fc2 <- tcga_AKT1_tt_extr %>%  
  mutate(., Gene=rownames(tcga_AKT1_tt_extr)) %>% 
  filter(., adj.P.Val < 0.05 & 2^abs(tcga_AKT1_tt_extr$logFC) >= 2) %>% 
  dplyr::select(., Gene)

tcga_AKT1_fc2 %>% dim
```

Volcano plot.

```{r}
#limma::volcanoplot(tcga_AKT1_fit_extr, coef = "highVSlow")

#pdf("tcga_akt1_volcano.pdf", height=4)
a <- ggplot(tcga_AKT1_tt_extr, aes(x= logFC, y = -log10(adj.P.Val))) + geom_point(alpha=1, size=0.5) + xlab("log2 fold change") + ylab("-log10 (adjusted p-value)") + xlim(-2, 2)
b <- a + geom_vline(xintercept= c(-1, 1), color = "red")
b + geom_hline(yintercept= 1.301, color = "red") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
#dev.off()
```

# Convert gene symbols to Ensembl.

Create and data frame where genes symbols matched to their ensembl code (using toptable object - tcga_AKT1_tt_extr).

```{r}
tcga_AKT1_sym2ens_extr <- AnnotationDbi::select(org.Hs.eg.db, keys = rownames(tcga_AKT1_tt_extr), columns = "ENSEMBL", keytype = "SYMBOL", multiVals ='first')
tcga_AKT1_sym2ens_extr %>% head
```

Check the length, they need to be the same to assign row names as ensembl codes.

```{r}
tcga_AKT1_sym2ens_extr %>% nrow
tcga_AKT1_tt_extr %>% nrow
```

Matching between genes and ensembl occur 1:many, can correct this by matching genes to the first listed ensembl.

```{r}
tcga_AKT1_sym2ens_extr <- tcga_AKT1_sym2ens_extr[ match(rownames(tcga_AKT1_tt_extr), tcga_AKT1_sym2ens_extr[,1]) ,2]
```

Again, check the length as it should be the same now.

```{r}
tcga_AKT1_sym2ens_extr %>% length
tcga_AKT1_tt_extr %>% nrow
```

Add ensembl code (AKT1_sym2ens) to the topTable from limma (tcga_AKT1_tt) as rownames.

```{r}
tcga_AKT1_tt_en_extr <- cbind(tcga_AKT1_tt_extr, tcga_AKT1_sym2ens_extr)
tcga_AKT1_tt_en_extr <- tcga_AKT1_tt_en_extr %>% na.omit()
tcga_unique_en_extr <- tcga_AKT1_tt_en_extr$tcga_AKT1_sym2ens_extr %>% as.character %>% make.unique()
tcga_AKT1_tt_en_extr <- cbind(tcga_AKT1_tt_en_extr, tcga_unique_en_extr)
rownames(tcga_AKT1_tt_en_extr) <- tcga_AKT1_tt_en_extr$tcga_unique_en_extr
tcga_AKT1_tt_en_extr %>% head()
tcga_AKT1_tt_en_extr <- tcga_AKT1_tt_en_extr[,1:6]
```

Pull the significant differentially expressed genes

```{r}
sum(tcga_AKT1_tt_en_extr$adj.P.Val<0.05)
```

Pull a list of the genes with an adjusted P value < 0.05.

```{r}
tcga_AKT1_sigGen_en_extr <- tcga_AKT1_tt_en_extr %>%  
  mutate(., Gene=rownames(tcga_AKT1_tt_en_extr)) %>% 
  filter(., adj.P.Val < 0.05) %>% 
  dplyr::select(., Gene)

tcga_AKT1_sigGen_en_extr %>% dim
tcga_AKT1_sigGen_en_extr %>% head
```

Significant genes with a FC above two (negative or positive) with Ensembl IDs.

```{r}
tcga_AKT1_fc2_en <- tcga_AKT1_tt_en_extr %>%  
   mutate(., Gene=rownames(tcga_AKT1_tt_en_extr)) %>% 
  filter(., adj.P.Val < 0.05 & 2^abs(tcga_AKT1_tt_en_extr$logFC) >= 2) %>% 
  dplyr::select(., Gene)

tcga_AKT1_fc2_en %>% dim
tcga_AKT1_fc2_en %>% head
```



Key output:
tcga_AKT1_tt_extr - toptable output of differentially expressed genes between AKT3 high and AKT3 low groups (GENE SYMBOLS)
tcga_AKT1_tt_en_extr - toptable output of differentially expressed genes between AKT3 high and AKT3 low groups (ENSEMBL)
tcga_AKT1_sigGen_extr - list of significantly differentially expressed genes between AKT3 high and AKT3 low groups (GENE SYMBOLS)
tcga_AKT1_sigGen_en_extr - list of significantly differentially expressed genes between AKT3 high and AKT3 low groups (ENSEMBL)
tcga_AKT1_fc2 - list of significantly differentially expressed genes between AKT3 high and AKT3 low groups with a FC more than 2 (GENE SYMBOLS)
tcga_AKT1_fc2_en - list of significantly differentially expressed genes between AKT3 high and AKT3 low groups with a FC more than 2 (ENSEMBL)
