---
title: "TCGA_setup"
author: "Jacqui Perkinson"
date: "31/03/2019"
output: html_document
---

Load required packages

```{r}
library(here)
library(dplyr)
library(ggplot2)

options(width=80)
```

# TCGA Gastric Cancer data set.

Load TCGA data set

```{r}
load('~/Desktop/Gastric_Cancer_Datasets/Data/tcga_gastric_cancer.RData')
```

What sort of objects are these?

```{r}
tcga_clinDat %>% class # clinical data
tcga_expDat %>% class # expression data, row names - gene symbols and columns - tumours.
```

Dimensions.

```{r}
tcga_clinDat %>% dim
tcga_expDat %>% dim
```

Show the variable names for clinical data set.

```{r}
tcga_clinDat %>% names
```

dfsEvent: Disease Free Survival Event (0,1)
dfsTime: Time of Disease Free Survival Event (months)
lc: Lauren Classification
molSub: Molecular Subtype (Cristescu et al)
stage: tumour stage
region: anatomic region of tumour
gender: patient gender
ageCat: patient age category
extra groups in tcga - hyplori, cdh1mut, EMTgroup.

The sample names should be included with the clinical data (but they are not). The samples are in the same order as in the expresion data, so they can be add as a new variable.

```{r}
tcga_clinDat <- tcga_clinDat %>% mutate(., PatID = colnames(tcga_expDat))
```

Now we have patients IDs in a column called PatID. 

```{r}
tcga_clinDat %>% head
```

Table of Lauren Class data.

```{r}
tcga_clinDat$lc %>% table
```

Table of Lauren Class versus Molecular Subtype.

```{r}
table(tcga_clinDat$lc, tcga_clinDat$molSub)
table(tcga_clinDat$PatID, tcga_clinDat$lc) %>% head
```

Note: Can "attach" clinical data to make the variables more accessible. Now the variables can be referenced directly.

```{r}
attach(tcga_clinDat)
```

# Plots.

Look at the expression of three genes (CDH1, AKT1, and AKT3) and their relationship with different subtypes.

### Gene - CHD1.

Extract expression information for CDH1.

```{r}
tcga_CDH1_data <- tcga_expDat[rownames(tcga_expDat) == "CDH1"]
```

Histogram of the CDH1 data

```{r}
#pdf("tcgacdhhist.pdf", height = 4)
tcga_CDH1_data %>% as.data.frame() %>%  
  ggplot(aes(x=.)) + 
  geom_histogram() + ylim(0,100) + scale_x_continuous(breaks=seq(-2,14,by=2)) + 
  ggtitle("E-cadherin (CDH1) expression") +
  xlab("Log2 expression of CDH1 in TCGA") +
  ylab("Frequency") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
#dev.off
```

Boxplot of CDH1 expression versus Molecular Subtype

```{r}
cbind(tcga_CDH1_data, as.factor(molSub)) %>% as.data.frame() %>%  
  ggplot(aes(x=molSub, y=tcga_CDH1_data, group=molSub, colour=molSub)) + 
  geom_boxplot() + 
  ggtitle("E-cadherin (CDH1) expression versus molecular subtype") +
  xlab("Molecular Subtype") +
  ylab("Log2 expression")
```

Plot the spread of CDH1 in the TCGA data set.

```{r}
#pdf("tcgacdhden.pdf", height = 4)
plot(density(tcga_expDat[,1]))
points(tcga_CDH1_data, rep(0, length(tcga_CDH1_data)), col='red', pch=16, cex=0.5)
#dev.off
```

### Gene - AKT1.

Extract expression information for AKT1.

```{r}
tcga_AKT1_data <- tcga_expDat[rownames(tcga_expDat) == "AKT1"]
```

Histogram of the AKT1 data

```{r}
#pdf("tcgaakt1hist.pdf", height = 4)
tcga_AKT1_data %>% as.data.frame() %>%  
  ggplot(aes(x=.)) + 
  geom_histogram() + 
  ggtitle("Protein Kinase B isoform 1 (AKT1) expression") +
  xlab("Log2 expression of AKT1 in TCGA") + 
  ylab("Frequency") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black"))
#dev.off
```

Boxplot of AKT1 expression versus Molecular Subtype

```{r}
cbind(tcga_AKT1_data, as.factor(molSub)) %>% as.data.frame() %>%  
  ggplot(aes(x=molSub, y=tcga_AKT1_data, group=molSub, colour=molSub)) + 
  geom_boxplot() + 
  ggtitle("Protein Kinase B isoform 1 (AKT1) expression versus molecular subtype") +
  xlab("Molecular Subtype") +
  ylab("Log2 expression")
```

Plot the spread of AKT1 in the TCGA data set.

```{r}
#pdf("tcgaakt1den.pdf", height = 4)
plot(density(tcga_expDat[,1]))
points(tcga_AKT1_data, rep(0, length(tcga_AKT1_data)), col='red', pch=16, cex=0.5)
#dev.off
```

### Gene - AKT3.

Extract expression information for AKT3.

```{r}
tcga_AKT3_data <- tcga_expDat[rownames(tcga_expDat) == "AKT3"]
```

Histogram of the AKT3 data

```{r}
#pdf("tcgaakt3hist.pdf", height = 4)
tcga_AKT3_data %>% as.data.frame() %>%  
  ggplot(aes(x=.)) + 
  geom_histogram() + 
  ggtitle("Protein Kinase B isoform 3 (AKT3) expression") +
  xlab("Log2 expression of AKT3 in TCGA") +
  ylab("Frequency") + theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), panel.background = element_blank(), axis.line = element_line(colour = "black")) +
  ylim(c(0,40))
#dev.off
```

Boxplot of AKT3 expression versus Molecular Subtype

```{r}
cbind(tcga_AKT3_data, as.factor(molSub)) %>% as.data.frame() %>%  
  ggplot(aes(x=molSub, y=tcga_AKT3_data, group=molSub, colour=molSub)) + 
  geom_boxplot() + 
  ggtitle("Protein Kinase B isoform 3 (AKT3) expression versus molecular subtype") +
  xlab("Molecular Subtype") +
  ylab("Log2 expression")
```

Plot the spread of AKT3 in the TCGA data set.

```{r}
#pdf("tcgaakt3den.pdf", height = 4)
plot(density(tcga_expDat[,1]))
points(tcga_AKT3_data, rep(0, length(tcga_AKT3_data)), col='red', pch=16, cex=0.5)
#dev.off
```



Key outputs: 
tcga_clinDat - TCGA clinical data.
tcga_expDat - TCGA expression data.
tcga_CDH1_data - TCGA CDH1 expression data.
tcga_AKT1_data - TCGA AKT1 expression data.
tcga_AKT3_data - TCGA AKT3 expression data.

