---
title: "TCGA_goseq_AKT3_3rds"
author: "Jacqui Perkinson"
date: "10/04/2019"
output: html_document
---

Load packages.

```{r}
library(goseq)
library(dplyr)
library(ggplot2)
```

# Load TCGA AKT3 (3rds) limma output objects.

Load the objects for goseq.

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/TCGA_AKT3_3rds_limma_output.Rdata")
```

# GoSeq using the limma output of differentially expressed genes between high AKT3 and low AKT3 expression groups (split by 3rds).

Format the the topTable tcga_AKT3_tt_en_extr) object from limma into a vector that is suitable for goseq.

```{r}
tcga_AKT3_genes <- as.integer(p.adjust(tcga_AKT3_tt_en_extr$P.Value[tcga_AKT3_tt_en_extr$logFC!=0], method = "BH")<.05)
names(tcga_AKT3_genes) <- row.names(tcga_AKT3_tt_en_extr[tcga_AKT3_tt_en_extr$logFC!=0,])
table(tcga_AKT3_genes)
```

Fit the probability weighting function (PWF).

```{r}
#pdf("goseqbiasakttcga.pdf", height=4)
tcga_AKT3_pwf <- nullp(tcga_AKT3_genes, "hg19", "ensGene")
tcga_AKT3_pwf %>% head
#dev.off()
```

Use the Wallenius approximation (default method) to calculate the over/under expressed GO groups in the differentially expressed genes.

```{r}
tcga_AKT3_wall <- goseq(tcga_AKT3_pwf, "hg19", "ensGene")
tcga_AKT3_wall %>% head
```

# Interpret the results from the GO analysis (using the Wallenius approximation).

To add the genes that are in the GO categories, make a loop to pull the genes out of numDEInCat. What is in numDEInCat.

```{r}
genelists <- function(tcga_AKT3_pwf, goterms, genome, ids){
  gene2cat <- getgo(rownames(tcga_AKT3_pwf), genome, ids)
  cat2gene <- split(rep(names(gene2cat), sapply(gene2cat, length)),
                    unlist(gene2cat, use.names = FALSE))
  out <- list()
  for(term in goterms){
    tmp <- tcga_AKT3_pwf[cat2gene[[term]],]
    tmp <- rownames(tmp[tmp$DEgenes > 0, ])
    out[[term]] <- tmp
  }
  out
}

goterms <- tcga_AKT3_wall$category
tcga_AKT3_go_list <- genelists(tcga_AKT3_pwf, goterms, "hg19", "ensGene")
```

Add columns to tcga_AKT3_wall; over-represented adjusted P values and under-represented adjusted P values. 

```{r}
tcga_AKT3_wall$over_represented_adj_pvalue <- p.adjust(tcga_AKT3_wall$over_represented_pvalue, method = "BH")
tcga_AKT3_wall$under_represented_adj_pvalue <- p.adjust(tcga_AKT3_wall$under_represented_pvalue, method = "BH")
```

### GO over-represented genes.

Pull GO categories that are signifcantly over represented below a 0.05 FDR cutoff. Then, add the over represented GO categories to tcga_AKT3_wall.

```{r}
tcga_AKT3_goCats_over <- tcga_AKT3_wall$category[p.adjust(tcga_AKT3_wall$over_represented_pvalue, method = "BH")<0.05]
tcga_AKT3_goCats_over %>% length
tcga_AKT3_over <- merge(tcga_AKT3_goCats_over, tcga_AKT3_wall, by =1)
tcga_AKT3_over %>% head
```

List the GO categories.

```{r}
tcga_AKT3_overNames <- tcga_AKT3_over %>% dplyr::select(., x) %>% unlist()
```

Loop that will run through the GO categories and pull the significant genes that are relevant for that category.

```{r}
sigGOgenes <- c()
for(gt in tcga_AKT3_overNames){
  GOiden <- tcga_AKT3_go_list[gt] %>% unlist()
  GOiden_en <- AnnotationDbi::select(org.Hs.eg.db, keys=GOiden, columns="SYMBOL", keytype = "ENSEMBL") %>% 
    na.omit()
  sigGOgenes <- c(sigGOgenes,
                  paste(GOiden_en[,2], sep="", collapse="::"))
}


tcga_AKT3_over$genes <- sigGOgenes
```

Edit the table (e.g. the order of the columns).

```{r}
tcga_AKT3_over <- tcga_AKT3_over[,c(1,6,7,4,5,2,8,3,9,10)]
colnames(tcga_AKT3_over) <- c("GO Category", "GO Term", "Ontology", 
                             "Number of Differentially Expressed Genes in Category", "Total Number of Genes in Category",
                             "P.Value for Over-represented Differentially Expressed Genes", "Adjusted P.Value for Over-represented Differentially Expressed Genes",
                             "P.Value for Under-represented Differentially Expressed Genes", "Adjusted P.Value for Under-represented Differentially Expressed Genes",
                             "List of Differentially Expressed Genes in Category")

tcga_AKT3_over %>% head
```

### GO under-represented genes.

Pull GO categories that are signifcantly under represented below a 0.05 FDR cutoff. Then, add the under represented GO categories to tcga_AKT3_wall.

```{r}
tcga_AKT3_goCats_under <- tcga_AKT3_wall$category[p.adjust(tcga_AKT3_wall$under_represented_pvalue, method = "BH")<0.05]
tcga_AKT3_goCats_under %>% length
tcga_AKT3_under <- merge(tcga_AKT3_goCats_under, tcga_AKT3_wall, by =1)
tcga_AKT3_under %>% head
```

List the GO categories.

```{r}
tcga_AKT3_underNames <- tcga_AKT3_under %>% dplyr::select(., x) %>% unlist()
```

Loop that will run through the GO categories and pull the significant genes that are relevant for that category.

```{r}
sigGOgenes <- c()
for(gt in tcga_AKT3_underNames){
  GOiden <- tcga_AKT3_go_list[gt] %>% unlist()
  GOiden_en <- AnnotationDbi::select(org.Hs.eg.db, keys=GOiden, columns="SYMBOL", keytype = "ENSEMBL") %>% 
    na.omit()
  sigGOgenes <- c(sigGOgenes,
                  paste(GOiden_en[,2], sep="", collapse="::"))
}


tcga_AKT3_under$genes <- sigGOgenes
```

Edit the table (e.g. the order of the columns).

```{r}
tcga_AKT3_under <- tcga_AKT3_under[,c(1,6,7,4,5,3,9,2,8,10)]
colnames(tcga_AKT3_under) <- c("GO Category", "GO Term", "Ontology", 
                              "Number of Differentially Expressed Genes in Category", "Total Number of Genes in Category",
                              "P.Value for Under-represented Differentially Expressed Genes", "Adjusted P.Value for Under-represented Differentially Expressed Genes",
                              "P.Value for Over-represented Differentially Expressed Genes", "Adjusted P.Value for Over-represented Differentially Expressed Genes",
                              "List of Differentially Expressed Genes in Category")

tcga_AKT3_under %>% head


#write.csv(tcga_AKT3_under, file = "GO_TCGA_AKT3_all_under.csv")
#write.csv(tcga_AKT3_over, file = "GO_TCGA_AKT3_all_over.csv")
```



Key outputs:
write.csv(tcga_AKT3_under, file = "GO_TCGA_AKT3_under.csv")
write.csv(tcga_AKT3_over, file = "GO_TCGA_AKT3_over.csv")
