---
title: "venn_AKT_genelists"
author: "Jacqui Perkinson"
date: "7/26/2019"
output: html_document
---

Load required packages.

```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(VennDiagram)
library(org.Hs.eg.db)
library(UpSetR)
```

Load required objects.

```{r}
load("~/Desktop/Gastric_Cancer_Datasets/Saved/GSE_AKT1_3rds_limma_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/GSE_AKT3_3rds_limma_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/TCGA_AKT1_3rds_limma_output.Rdata")
load("~/Desktop/Gastric_Cancer_Datasets/Saved/TCGA_AKT3_3rds_limma_output.Rdata")
```

# Find genes that only associate with AKT3 (filtering on fold change)

```{r}
ven <- list("GSE AKT1 Genes (Sig)" = gse_AKT1_sigGen_en_extr[,1], "TCGA AKT1 Genes (sig)" = tcga_AKT1_sigGen_en_extr[,1], "GSE AKT3 Genes (FC > 2)" = gse_AKT3_fc2_en[,1], "TCGA AKT3 Genes (FC > 2)" = tcga_AKT3_fc2_en[,1])
gplots::venn(ven)
```

Upset plot (shows 51 genes that associate with AKT3)

```{r}
pdf("51upset.pdf", height=4)
listInput_1 <- list("TCGA AKT3 Genes (FC)" = tcga_AKT3_fc2_en[,1], "GEO AKT3 Genes (FC)" = gse_AKT3_fc2_en[,1], "TCGA AKT1 Genes" = tcga_AKT1_sigGen_en_extr[,1],"GEO AKT1 Genes" = gse_AKT1_sigGen_en_extr[,1])

UpSetR::upset(fromList(listInput_1), order.by = "freq", mainbar.y.max = 5000, text.scale = 1.3)
dev.off()

pdf("3485upset.pdf", height=4)
listInput_2 <- list("TCGA AKT3 Genes" = tcga_AKT3_sigGen_en_extr[,1], "GEO AKT3 Genes" = gse_AKT3_sigGen_en_extr[,1], "TCGA AKT1 Genes" = tcga_AKT1_sigGen_en_extr[,1], "GEO AKT1 Genes" = gse_AKT1_sigGen_en_extr[,1])

UpSetR::upset(fromList(listInput_2), order.by = "freq", text.scale = 1.3)
dev.off
```

Find the intersect between GSE and TCGA AKT3 genes with FC > 2.

```{r}
AKT3_FC <- intersect(tcga_AKT3_fc2_en[,1], gse_AKT3_fc2_en[,1])
AKT3_FC %>% head
```

Group GSE and TCGA AKT1 significant genes.

```{r}
AKT1_sig <- union(gse_AKT1_sigGen_en_extr[,1], tcga_AKT1_sigGen_en_extr[,1])
AKT1_sig %>% head
```

Find the difference between all AKT1 genes and AKT3 genes with FC > 2.

```{r}
AKT3_only <- setdiff(AKT3_FC, AKT1_sig)
AKT3_only
```

51 genes.

### Convert from ensembl to gene symbols

Create and object with genes matched to their ensembl code (using AKT3_only).

```{r}
AKT3_only_gsym <- as.data.frame(AKT3_only)
rownames(AKT3_only_gsym) <- AKT3_only_gsym[,1]

gsym <- AnnotationDbi::select(org.Hs.eg.db, keys = rownames(AKT3_only_gsym), columns = "SYMBOL", keytype = "ENSEMBL", multiVals ='first')
gsym %>% head
gsym %>% dim
```

1:1 Mapping

```{r}
AKT3_final <- gsym[,2]
AKT3_final %>% length
AKT3_final %>% class
AKT3_final %>% sort
```

Formatting the list of genes

```{r}
# cat(AKT3_final, sep = '\n')
# cat(AKT3_final)

# sink("~/Desktop/AKT3_sig_fc.txt")
# print(cat(AKT3_final, sep = '\n'))
# sink()
```



# For gene ontology - find genes that only associate with AKT3 (without filtering on fold change)

Compare GSE AKT1, GSE AKT3, TCGA AKT1, TCGA AKT3 significant genes. 

```{r}
ven <- list("GSE AKT1 Genes (sig)" = gse_AKT1_sigGen_en_extr[,1], "TCGA AKT1 Genes (sig)" = tcga_AKT1_sigGen_en_extr[,1], "GSE AKT3 Genes (sig)" = gse_AKT3_sigGen_en_extr[,1], "TCGA AKT3 Genes (sig)" = tcga_AKT3_sigGen_en_extr[,1])
gplots::venn(ven)
```

Upset plot (shows 3485 genes that associate with AKT3, not filtered by FC)

```{r}
#pdf("3485upset.pdf", height=4)
listInput_2 <- list("GEO AKT1 Genes (sig)" = gse_AKT1_sigGen_en_extr[,1], "TCGA AKT1 Genes (sig)" = tcga_AKT1_sigGen_en_extr[,1], "GSE AKT3 Genes (sig)" = gse_AKT3_sigGen_en_extr[,1], "TCGA AKT3 Genes (sig)" = tcga_AKT3_sigGen_en_extr[,1])

UpSetR::upset(fromList(listInput_2), order.by = "freq")
#dev.off

pdf("allupset.pdf", height = 5, width = 8)
listInput_all <- list("TCGA AKT3 Genes (FC)" = tcga_AKT3_fc2_en[,1], "GEO AKT3 Genes (FC)" = gse_AKT3_fc2_en[,1], "TCGA AKT3 Genes" = tcga_AKT3_sigGen_en_extr[,1], "GEO AKT3 Genes" = gse_AKT3_sigGen_en_extr[,1],"TCGA AKT1 Genes" = tcga_AKT1_sigGen_en_extr[,1], "GEO AKT1 Genes" = gse_AKT1_sigGen_en_extr[,1])

UpSetR::upset(fromList(listInput_all), nsets = 6, order.by = "freq")
dev.off


```

Find the intersect between GSE and TCGA AKT3 genes

```{r}
AKT3_gns <- intersect(gse_AKT3_sigGen_en_extr[,1], tcga_AKT3_sigGen_en_extr[,1])
AKT3_gns %>% head
```

Group GSE and TCGA AKT1 significant genes.

```{r}
AKT1_gns <- union(gse_AKT1_sigGen_en_extr[,1], tcga_AKT1_sigGen_en_extr[,1])
AKT1_gns %>% head
```

Find the difference between all AKT1 genes and AKT3 genes

```{r}
AKT3_only_allsig <- setdiff(AKT3_gns, AKT1_gns)
AKT3_only_allsig %>% length()
```

3485 genes.

### Convert ensembl to gene symbols.

Create and object with genes matched to their ensembl code (using AKT3_only_allsig).

```{r}
AKT3_only_allsig_gsym <- as.data.frame(AKT3_only_allsig)
rownames(AKT3_only_allsig_gsym) <- AKT3_only_allsig_gsym[,1]

gsym_all <- AnnotationDbi::select(org.Hs.eg.db, keys = rownames(AKT3_only_allsig_gsym), columns = "SYMBOL", keytype = "ENSEMBL", multiVals ='first')
gsym_all %>% head
gsym_all %>% dim
```

1:many mapping

```{r}
AKT3_allsig <- gsym_all[,2]
AKT3_allsig %>% length
AKT3_allsig %>% class
```

Formatting the list of genes

```{r}
# cat(AKT3_allsig, sep = '\n')
# cat(AKT3_allsig)

# sink("~/Desktop/AKT3_sig_all.txt")
# print(cat(AKT3_allsig, sep = '\n'))
# sink()
```



# For gene ontology - find genes that only associate with AKT1 (without filtering on fold change - as there are zero genes with FC > 2).

```{r}
ven_1 <- list("GSE AKT3 Genes (sig)" = gse_AKT3_sigGen_en_extr[,1], "TCGA AKT3 Genes (sig)" = tcga_AKT3_sigGen_en_extr[,1], "GSE AKT1 Genes (sig)" = gse_AKT1_sigGen_en_extr[,1], "TCGA AKT1 Genes (sig)" = tcga_AKT1_sigGen_en_extr[,1])
gplots::venn(ven_1)
```

Upset plot (shows 190 genes that associate with AKT1, not filtered by FC)

```{r}
#pdf("190upset.pdf", height=4)
listInput_3 <- list("GSE AKT3 Genes (sig)" = gse_AKT3_sigGen_en_extr[,1], "TCGA AKT3 Genes (sig)" = tcga_AKT3_sigGen_en_extr[,1], "GSE AKT1 Genes (sig)" = gse_AKT1_sigGen_en_extr[,1], "TCGA AKT1 Genes (sig)" = tcga_AKT1_sigGen_en_extr[,1])

UpSetR::upset(fromList(listInput_3), order.by = "freq")
#dev.off()
```

Find the intersect between GSE and TCGA AKT1 genes

```{r}
AKT1_all <- intersect(tcga_AKT1_sigGen_en_extr[,1], gse_AKT1_sigGen_en_extr[,1])
AKT1_all %>% head
```

Group GSE and TCGA AKT3 significant genes.

```{r}
AKT3_all <- union(gse_AKT3_sigGen_en_extr[,1], tcga_AKT3_sigGen_en_extr[,1])
AKT3_all %>% head
```

Find the difference between all AKT1 genes and AKT3 genes.

```{r}
AKT1_only_allsig <- setdiff(AKT1_all, AKT3_all)
AKT1_only_allsig %>% length()
```

190 genes.

### Convert to gene symbols from ensembl

Create and object with genes matched to their ensembl code (using AKT3_only).

```{r}
AKT1_only_gsym <- as.data.frame(AKT1_only_allsig)
rownames(AKT1_only_gsym) <- AKT1_only_gsym[,1]

gsym_1 <- AnnotationDbi::select(org.Hs.eg.db, keys = rownames(AKT1_only_gsym), columns = "SYMBOL", keytype = "ENSEMBL", multiVals ='first')
gsym_1 %>% head
gsym_1 %>% dim
```

1:1 Mapping

```{r}
AKT1_final <- gsym_1[,2]
AKT1_final %>% length
AKT1_final %>% class
```

Formatting the list of genes

```{r}
# cat(AKT1_final, sep = '\n')
# cat(AKT1_final)

# sink("~/Desktop/AKT1_sig_all.txt")
# print(cat(AKT1_final, sep = '\n'))
# sink()
```



# Match AKT3 genes (51) with FC values to help select druggable targets.

Get toptable values for 51 key AKT3 genes for TCGA data.

```{r}
tcga_gns_keep <- which(rownames(tcga_AKT3_tt_en_extr) %in% AKT3_only)
tcga_gns_keep %>% length()

tcga_tt_AKT3_keygenes <- tcga_AKT3_tt_en_extr[tcga_gns_keep,]
tcga_tt_AKT3_keygenes %>% dim()
tcga_tt_AKT3_keygenes %>% head

tcga_tt_AKT3_keygenes_gsym <- cbind(tcga_tt_AKT3_keygenes, gsym)
rownames(tcga_tt_AKT3_keygenes_gsym) <- tcga_tt_AKT3_keygenes_gsym$SYMBOL
tcga_tt_AKT3_keygenes_gsym <- tcga_tt_AKT3_keygenes_gsym[,1:6]
tcga_tt_AKT3_keygenes_gsym %>% head

#write.csv(tcga_tt_AKT3_keygenes_gsym, file = "tt51tcga.csv")
```

Get toptable values for 51 key AKT3 genes for GSE data.

```{r}
gse_gns_keep <- which(rownames(gse_AKT3_tt_en_extr) %in% AKT3_only)
gse_gns_keep %>% length()

gse_tt_AKT3_keygenes <- gse_AKT3_tt_en_extr[gse_gns_keep,]
gse_tt_AKT3_keygenes %>% dim()
gse_tt_AKT3_keygenes %>% head

gse_tt_AKT3_keygenes_gsym <- cbind(gse_tt_AKT3_keygenes, gsym)
rownames(gse_tt_AKT3_keygenes_gsym) <- gse_tt_AKT3_keygenes_gsym$SYMBOL
gse_tt_AKT3_keygenes_gsym <- gse_tt_AKT3_keygenes_gsym[,1:6]
gse_tt_AKT3_keygenes_gsym %>% head

#write.csv(gse_tt_AKT3_keygenes_gsym, file = "tt51geo.csv")
```

Key output:
AKT3_final - list of 51 genes (gene symbols)
AKT3_only - list of 51 genes (ensembl IDs)
AKT3_only_allsig - list of 3485 genes, not filtered by fold change (gene symbols)
AKT3_allsig - list of 3498 genes, not filtered by fold change (ensembl IDs)
AKT1_only_allsig - list of 190 genes, not filtered by fold change (gene symbols)
AKT1_final - list of 190 genes, not filtered by fold change (ensembl IDs)

tcga_tt_AKT3_keygenes - toptable of 51 genes for TCGA data (gene symbols)
tcga_tt_AKT3_keygenes_gsym - toptable of 51 genes for TCGA data (ensembl IDs)
gse_tt_AKT3_keygenes - toptable of 51 genes for GSE data (gene symbols)
gse_tt_AKT3_keygenes_gsym - toptable of 51 genes for GSE data (ensembl IDs


